A Global Genome-wide Scan with Optimal Cutoff Mining for Emerging Biomarkers in Head and Neck Squamous Cell Carcinoma

### 2021-03-10 main.tex
Updates from Overleaf

\begin{document}
%\begin{paracol}{2}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%\setcounter{section}{-1} %% Remove this when starting to work on the template.
%\section{How to Use this Template}

@@

%https://bmcmedgenomics.biomedcentral.com/articles/10.1186/s12920-019-0624-2
#XAI
Interpretable deep neural network for cancer survival analysis by integrating genomic and clinical data

@@

In personal history section of admission note for inpatient:\\
<Habits>\\
　　　　-Tobacco: 1.5 pack/day for 30 years\\
　　　　-Alcohol drinking: Occasionally\\
　　　　-Betel nuts: 30 nuts/day for 30 years\\
<Social/Economic Evaluation>\\
　　　　-Living condition: Living with family\\
　　　　-Family support: Well\\
　　　　-Main caregiver: Spouse\\
　　　　-Financial support: Sufficient\\
<Psychological Evaluation>\\
　　　　Stable but worry about this oral lesion\\
　　　　Suspected to be abuse or neglected victim: negative\\
<Spiritual Assessment>\\
　　　　Religion: Nil\\
　　　　Diagnosed with life-threatening diseases or terminal stage of chronic diseases or cancers?　No\\
% cancer cure (care) 的證明
%# 懺悔
We always educate our cancer patients that they should repentantly confess for not taking care of body and spirit in the pass, and sincere thanks for the hard work of our physical body. Mindfulness and meditation will be helpful in cancer healthcare.
Once holistic feature is available, graph convolutional neural network (GCNN) is mandatory for further survival analysis\cite{Ching2018}.
The microenvironment of HNSCC, influenced by the mind-brain-body axis, requires further exploration and understanding using this multi-parametric approach.
%  extreme pleasure, anger, overthinking, sadness, fear, shock, anxiety, depression, fatigue, stress
%七情: 喜、怒、思、悲、恐、驚、憂

@@

%=====================================
% References, variant A: external bibliography
%=====================================
\externalbibliography{yes}
%\bibliography{your_external_BibTeX_file}
%\bibliographystyle{model1-num-names}
\bibliography{TCGA_margin_cutoff.bib, Holistic.bib}

>>>>

\begin{document}
\begin{paracol}{2}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%\setcounter{section}{-1} %% Remove this when starting to work on the template.
%\section{How to Use this Template}

@@

%https://bmcmedgenomics.biomedcentral.com/articles/10.1186/s12920-019-0624-2
%#XAI
Interpretable deep neural network for cancer survival analysis by integrating genomic and clinical data

@@

In personal history section of admission note for inpatient:\\
<Habits>\\
　　　　-Tobacco: 1.5 pack/day for 30 years\\
　　　　-Alcohol drinking: Occasionally\\
　　　　-Betel nuts: 30 nuts/day for 30 years\\
<Social/Economic Evaluation>\\
　　　　-Living condition: Living with family\\
　　　　-Family support: Well\\
　　　　-Main caregiver: Spouse\\
　　　　-Financial support: Sufficient\\
<Psychological Evaluation>\\
　　　　Stable but worry about this oral lesion\\
　　　　Suspected to be abuse or neglected victim: negative\\
<Spiritual Assessment>\\
　　　　Religion: Nil\\
　　　　Diagnosed with life-threatening diseases or terminal stage of chronic diseases or cancers?　No\\
% cancer cure (care) 的證明
%# 懺悔
We always educate our cancer patients that they should repentantly confess for not taking care of body and spirit in the pass, and sincere thanks for the hard work of our physical body. Mindfulness and meditation will be helpful in cancer healthcare.
Once holistic feature is available, graph convolutional neural network (GCNN) is mandatory for further survival analysis\cite{Ching2018a}.
The microenvironment of HNSCC, influenced by the mind-brain-body axis, requires further exploration and understanding using this multi-parametric approach.
%  extreme pleasure, anger, overthinking, sadness, fear, shock, anxiety, depression, fatigue, stress
%七情: 喜、怒、思、悲、恐、驚、憂

@@

%=====================================
% References, variant A: external bibliography
%=====================================
\externalbibliography{yes}
%\bibliography{your_external_BibTeX_file}
%\bibliographystyle{model1-num-names}
\bibliography{TCGA_margin_cutoff.bib, Holistic.bib, Deep_Learning.bib}
